### 2008-12-21 talk/ecoop2009/clibackend.tex
remove space before of footnote
typo

At the moment of writing, three backends have been implemented: one for Intel
\emph{x86} processors, one for \emph{PowerPC} processors, and one for the
\emph{CLI Virtual Machine}.  The latter is special because instead of emitting
code for a real CPU it emits code for a virtual machine \footnote{By using the 
\lstinline{Reflection.Emit} namespace and creating \lstinline{DynamicMethod}s.}: 
before being
executed, the generated code will be compiled again by .NET's own JIT
compiler.

@@

As usual, the drawback is that programs that runs for a very short period of
time could run slower with JIT than without, due to the time spent doing the
initial (double) compilation.  It is important to underline that so far we
mostly focused making the JIT able to produce very fast code, without trying
to optimzed the compilation phase itself.

>>>>

At the moment of writing, three backends have been implemented: one for Intel
\emph{x86} processors, one for \emph{PowerPC} processors, and one for the
\emph{CLI Virtual Machine}.  The latter is special because instead of emitting
code for a real CPU it emits code for a virtual machine\footnote{By using the 
\lstinline{Reflection.Emit} namespace and creating \lstinline{DynamicMethod}s.}: 
before being
executed, the generated code will be compiled again by .NET's own JIT
compiler.

@@

As usual, the drawback is that programs that runs for a very short period of
time could run slower with JIT than without, due to the time spent doing the
initial (double) compilation.  It is important to underline that so far we
mostly focused making the JIT able to produce very fast code, without trying
to optimze the compilation phase itself.
